\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}


\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\Large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \if\relax\detokenize{#1}\relax
    \item{#2 \vspace{-2pt}}
  \else
    \item{
      \textbf{#1}: #2 \vspace{-2pt}
    }
  \fi
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeItemWithDate}[3]{
  \item
    \begin{tabular*}{#1\textwidth}{@{\extracolsep{\fill}} l r}
      #2 & \small\textit{#3} \\
    \end{tabular*}
}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://brandonyifanyang.com/}{\Large Brandon (Yifan) Yang}} & Email : \href{mailto:branyang@virginia.edu}{branyang@virginia.edu}\\
  \href{https://brandonyifanyang.com/}{brandonyifanyang.com}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{\href{https://engineering.virginia.edu/department/computer-science}{University of Virginia}}{Charlottesville, VA}
{B.S. in Computer Science;  Major GPA: 3.98/4.00; Cumulative GPA: 3.91/4.00}{August 2021 - May 2025}
\item \textbf{Relevant Coursework}: ML, RL (G), NLP (G), Probabilistic ML (G), Human-Robot Interaction (G), Optimization, Data Structures
\& Algorithms, Theory of Computation, Computer Systems Organization, Software Engineering
\resumeSubHeadingListEnd


%-----------RESEARCH EXPERIENCE--------
\section{Research Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Learning and Interactive Robotics, University of Virginia}{Charlottesville, VA}
{Advisor: \href{https://yenlingkuo.com/}{Prof. Yen-Ling Kuo}}{Aug 2024 - Present}
\resumeItemListStart
\resumeItem{Ongoing Senior Capstone}
{Vision-Language-Action (VLA) model for robotic manipulation.}
\item Investigating VLA model outputting both language and corresponding actions within a unified transformer output space, grounding both domains simultaneously at each time step.
\resumeItemListEnd


\resumeSubheading
{University of Maryland}{College Park, MD}
{Advisor: \href{https://jbhuang0604.github.io/}{Prof. Jia-Bin Huang}}{May 2024 - Present}
\resumeItemListStart
\item \textbf{Semantically Aware 3D Gaussian Splatting}
\begin{itemize}
  \item Developed novel method to inject semantically aware embeddings into 3D Gaussian Splatting (3DGS) scenes for 3D understanding and segmentation tasks.
  \item Leveraged video segmentation from SAMv2 to maintain temporal consistency in injection of CLIP features from 2D training set to 3DGS scene, ensuring stable and accurate 3D embeddings.
\end{itemize}

\resumeItemListEnd


\resumeSubheading
{Collaborative Robotics Lab, University of Virginia}{Charlottesville, VA}
{Advisor: \href{https://www.tiqbal.com/}{Prof. Tariq Iqbal}}{May 2022 - May 2024}
\resumeItemListStart
\item \textbf{Grounded Location for Object Manipulation (GLOMA)}
\begin{itemize}
  \item Zero-shot image-editing model grounded by language instructions for object relocation and manipulation tasks, designed for downstream robotic applications using goal-conditioned RL.
  \item Integrated language grounding with visual perception using bounding box guidance from pre-trained language models, enabling precise object relocation without external supervision.
  \item Collected and annotated custom dataset for fine-tuning pre-trained language and vision models.
\end{itemize}
\item \textbf{Centralized multi-agent RL for Collaborative Tasks}
\begin{itemize}
  \item Developed long-horizon on/offline centralized MARL for robotic bolt screwing tasks.
  \item Designed and optimized custom reward functions in multi-agent framework for task completion and agent collaboration.
  \item Deployed and tested custom simulated environments in IsaacGym for training and evaluation.
\end{itemize}
\resumeItemListEnd
\resumeSubHeadingListEnd



%-----------TEACHING EXPERIENCE-----------------
\section{Teaching Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Teaching Assistant}{}
{Machine Learning w/ Prof. Rich Nguyen}{August 2024 - Present}
\resumeItemListStart
\resumeItem{}
{Authored comprehensive and interactive course notes to support student learning and understanding.}
\resumeItemListEnd
\resumeSubheading
{Teaching Assistant}{}
{Theory of Computation w/ Prof. Mark Floryan}{Jan 2024 - May 2024}
\resumeItemListStart
\resumeItem{}
{Held weekly office hours and review sessions to assist students with course material.}
\resumeItemListEnd
\resumeSubheading
{Lab Lead Teaching Assistant}{}
{Computer Systems Organization w/ Prof. John Hott}{Jan 2023 - May 2023}
\resumeItemListStart
\resumeItem{}
{Led weekly lab sections with short lectures and hands-on activities for 70+ students.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------HONORS-----------------

\section{Honors}
\resumeSubHeadingListStart
\resumeItemWithDate{0.97}{\textbf{Dean's Engineering Research Scholarship (\$5000)}: University of Virginia}{May 2023}\vspace{-5pt}
\resumeItemWithDate{0.97}{\textbf{University of Virginia Research Computing Exhibition Finalist}: University of Virginia}{April 2024}\vspace{-5pt}
\resumeItemWithDate{0.97}{\textbf{Entrepreneurship Cup Winner (Received \$1000 in funding)}: University of Virginia}{November 2023}\vspace{-5pt}
\resumeItemWithDate{0.97}{\textbf{Dean's List}: University of Virginia}{}\vspace{-5pt}

\resumeSubHeadingListEnd




%-----------Presentations-----------------
\section{Presentations}
\resumeSubHeadingListStart
\resumeItem{}{\textbf{Mechanistic Interpretability in Large Language Models}}\vspace{-4pt}
\begin{itemize}
  \resumeItemWithDate{0.925}{University of Virginia Research Computing Exhibition, Charlottesville, VA}{April 2024}
\end{itemize}\vspace{-9pt}
\resumeItem{}{\textbf{GLOMA: Grounded Location for Object Manipulation}}\vspace{-4pt}
\begin{itemize}
  \resumeItemWithDate{0.925}{University of Virginia Fall Engineering Research Expo, Charlottesville, VA}{October 2023}
  \resumeItemWithDate{0.925}{University of Virginia Spring Thornton Society Dinner, Charlottesville, VA}{September 2023}
  \resumeItemWithDate{0.925}{University of Virginia Summer Research Symposium, Charlottesville, VA}{July 2023}
\end{itemize}\vspace{-9pt}
\resumeItem{}{\textbf{Robot Tool Grasping with AprilTag}}\vspace{-4pt}
\begin{itemize}
  \resumeItemWithDate{0.925}{University of Virginia Engineering Open House, Charlottesville, VA}{November 2023}
  \resumeItemWithDate{0.925}{University of Virginia Engineering Open House, Charlottesville, VA}{November 2022}
\end{itemize}\vspace{-9pt}
\resumeSubHeadingListEnd




%-----------SOFTWARE PROJECTS-----------------
\section{Software Projects}
\resumeSubHeadingListStart
\resumeSubItem{\href{https://notie-markdown.vercel.app/}{notie-markdown}}
{Open-source React component for Markdown rendering, built with TypeScript.}
\resumeSubItem{SmartOH}
{AI-assisted office hour queueing system, built with Python, PyTorch, and TypeScript. Placed 3rd overall at VTHacks11 (3/393).}
\resumeSubItem{Voy}
{Collaborated with 7 non-profits to develop Voy, a volunteer and driver management platform using Python and TypeScript; received funding from UVA's Entrepreneurship Cup.}
\resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
\resumeSubItem{Languages}
{Python, C/C++, Java, JavaScript, TypeScript, HTML/CSS}
\resumeSubItem{Technologies}
{PyTorch, TensorFlow, Linux, Git, Docker, \LaTeX}
\resumeSubItem{Web Tools}
{React, Node.js, Express, Django}

\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
