\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{array}
\usepackage{setspace}
\usepackage{multirow}

\singlespacing
% \setstretch{1.1}
% \onehalfspacing

\setlist[itemize]{itemsep=0em, topsep=0em, leftmargin=*}

\definecolor{linkblue}{rgb}{0, 0, 1}


% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% Sections formatting, reduced vertical space before and after each section.
\titleformat{\section}{
    \scshape\raggedright\Large 
}{}{0em}{}[\color{black}\titlerule]
\titlespacing*{\section}{0pt}{5pt}{5pt} % left, before-skip, after-skip

%-------------------------Custom commands-------------------------

% Link defaulted to black unless using \linkhref
\newcommand{\linkhref}[2]{\textcolor{linkblue}{\href{#1}{#2}}} 

% Date in small italics
\newcommand{\Date}[1]{\textit{\small #1}}

% Heading with 4 arguments: #1: Title, #2: Location, #3: Subtitle, #4: Date
\newcommand{\heading}[4]{
  \textbf{#1} \hfill #2 \\
  \textit{\small#3} \hfill \Date{#4}
}

\newcommand{\headingjob}[4]{
  \textbf{#1} \hfill #2 \\
  \textit{#3} \hfill \Date{#4}
}


% % Heading with 3 arguments: #1: Title, #2: Location, #3: Date
% \newcommand{\simpleheading}[3]{%
%   \noindent
%   \begin{tabular*}{\linewidth}{@{\extracolsep{\fill}} l r}
%     \multirow{2}{*}[0pt]{\textbf{#1}} & #2 \\[-0.2ex]
%                                       & \Date{#3}
%   \end{tabular*}%
% }


\renewcommand{\labelitemi}{$\circ$} % First-level bullet points as circles
\renewcommand{\labelitemii}{$\circ$} % Second-level bullet points as circles

\begin{document}

\begin{tabular} {@{}l}
    \textbf{\href{https://brandonyifanyang.com/}{\Large{Brandon Yifan Yang}}} \\[3pt]
    \linkhref{https://brandonyifanyang.com/}{brandonyifanyang.com} \quad \linkhref{mailto:yang52@engineering.upenn.edu}{yang52@engineering.upenn.edu} \quad \linkhref{https://github.com/branyang02}{github.com/branyang02} \quad \linkhref{https://scholar.google.com/citations?user=dZny9s0AAAAJ&hl=en}{Google Scholar}
\end{tabular}


\section{Education}
\begin{itemize}
    \item \heading{University of Pennsylvania}{Philadelphia, PA}{M.S.E. in Robotics; GPA: 3.7/4.0}{May 2027}
    \item \heading{University of Virginia}{Charlottesville, VA}{B.S. in Computer Science; Highest Distinction; GPA: 3.9/4.0}{May 2025}
    \item \textbf{Selected Coursework}: Learning in Robotics, Reinforcement Learning, Probabilistic Machine Learning, GPU Programming \& Architecture, Physical Intelligence, Natural Language Processing
\end{itemize}

\section{Experience}
\begin{itemize}[label={}, leftmargin=0pt]
    \item \headingjob{Research Lead}{San Francisco, CA}{AfterQuery (YC W25)}{May 2026 - Present}
          \begin{itemize}
              \item Led development of custom UMI hardware and a distributed robot data collection system, integrating Rust-based device-side capture and LiDAR tracking with a server-side SLAM pipeline for end-effector tracking and automated storage with Hugging Face dataset management.
              \item Led a 6-person research team building a full-stack AI-agent search benchmark platform for task collection through model evaluation; evaluated frontier agent harnesses and models with rubric grading and trace logging.
          \end{itemize}
    \item \headingjob{Embodied Intelligence Research Intern}{Beijing, China}{Spirit AI}{May 2025 - Aug 2025}
          \begin{itemize}
              \item Trained and evaluated VLA policy variants in PyTorch across simulation and real dual-arm robot experiments, comparing contrastive objectives, observation-noise curricula, reduced guidance inputs, and mixture-of-experts architectures.
              \item Designed and implemented a DAgger data-collection pipeline for VLA models, including operator-takeover logic and corrective-demonstration workflows used for model training and evaluation.
              \item Built a reproducible Docker/Slurm pipeline for VLA simulation, training, and evaluation workflows; open-sourced code and datasets on \linkhref{https://github.com/Robot-VLA/lerobot-vla.git}{GitHub}.
          \end{itemize}
\end{itemize}

\section{Research Experience}
\begin{itemize}[label={}, leftmargin=0pt]
    \item \heading{\href{https://penn-pal-lab.github.io/}{Perception, Action, \& Learning Lab}, University of Pennsylvania}{Philadelphia, PA}
          {Advisor: Dinesh Jayaraman}{Aug 2025 - Present}
          \begin{itemize}
              \item Implemented demonstration retrieval for $\pi_{0.5}$ VLA policies, integrating robot data retrieval into training and test-time inference for tabletop manipulation experiments. (\textit{CoRL 2026})
              \item Engineered data transformation, training, and evaluation pipelines for retrieval-based VLA variants using JAX, PyTorch, Hugging Face, Docker, Slurm, and Ray.
              \item Designed activation-collection and activation-steering infrastructure for VLA analysis across MetaWorld, LIBERO, RoboCasa, and real Franka hardware experiments. (\textit{ICML 2026 Workshop; NeurIPS 2026})
          \end{itemize}
    \item \heading{Learning and Interactive Robotics, University of Virginia}{Charlottesville, VA}
          {Advisor: Yen-Ling Kuo}{Aug 2024 - May 2025}
          \begin{itemize}
              \item \textbf{SkillVLA}: Developed a skill-conditioned VLA model for language-conditioned manipulation, using subgoal instructions and a learned skill library to structure action generation.
              \item Presented SkillVLA as an oral talk at the 2024 UVA LLM Workshop (\linkhref{https://www.brandonyifanyang.com/skillvla.pdf}{slides}), earning the Audience Choice Award (top 3 of 28 presentations).
              \item \textbf{Contrastive Learning for Robot Manipulation}: Trained contrastive objectives over action sequences to learn behavior-grounded visual embeddings for visuomotor policies under varied camera poses and object appearances. (\linkhref{https://class-robot.github.io/}{CoRL 2025})
              \item Modified simulation environments and trained PyTorch visuomotor policies to evaluate learned behavior-grounded embeddings.
          \end{itemize}
    \item \heading{\href{https://www.collabrobotics.com/}{Collaborative Robotics Lab}, University of Virginia}{Charlottesville, VA}
          {Advisor: Tariq Iqbal}{May 2022 - May 2024}
          \begin{itemize}
              \item \textbf{\href{https://github.com/branyang02/GLOMA}{Grounded Location for Object Manipulation (GLOMA)}} [\linkhref{https://github.com/branyang02/GLOMA}{code}]: Led a team of 3 in developing a language-grounded image-editing pipeline for object relocation goals in robotic manipulation settings.
              \item Integrated language grounding with bounding-box-guided visual editing for object relocation.
              \item Collected and annotated a dataset for fine-tuning pre-trained language and vision models.
              \item \textbf{\href{https://github.com/branyang02/PandaFactory}{Centralized Multi-Agent RL for Collaborative Tasks}} [\linkhref{https://github.com/branyang02/PandaFactory}{code}]: Implemented offline and online centralized MARL training for long-horizon robotic bolt-screwing tasks in Isaac Gym.
              \item Designed custom multi-agent reward functions for task completion and collaboration, improving simulated task success by 20\% over the project baseline.
          \end{itemize}
\end{itemize}

\section{Publications}
\begin{itemize}[label={}, leftmargin=0pt]
    \item Jiani Huang*, \textbf{Brandon Y. Yang*}, Amish Sethi, Yuchen Zheng, Christopher Watson, Jianing Qian, Mayur Naik, and Dinesh Jayaraman. ``Retrieval-Augmented Vision-Language-Action Model." Under review at \textit{CoRL 2026}.
    \item Miranda Muqing Miao*, Subin Kim*, \textbf{Brandon Y. Yang*}, Dinesh Jayaraman, and Lyle Ungar. ``Contrastive Conceptor Activation Steering (COAST): Unlocking Vision-Language-Action Models through Hidden States." Accepted poster, \textit{ICML 2026 Mechanistic Interpretability Workshop}; submitted to \textit{NeurIPS 2026}. \hfill [\linkhref{https://mechinterpworkshop.com/posters/}{Workshop}][\linkhref{https://arxiv.org/abs/2605.17144}{arXiv}]
    \item Amish Sethi*, \textbf{Brandon Y. Yang*}, Michael Evans, Spencer Mateega, and Sam Jung. ``Position: Trust No Multi-Turn Benchmark Without Measuring Its User Simulator." Submitted to \textit{NeurIPS 2026 Position Paper Track}.
    \item Sung-Wook Lee, Xuhui Kang, \textbf{Brandon Y. Yang}, and Yen-Ling Kuo. ``CLASS: Contrastive Learning via Action Sequence Supervision for Robot Manipulation." \textit{Conference on Robot Learning}, pp. 4743--4766. PMLR, 2025. \hfill [\linkhref{https://class-robot.github.io/}{Website}][\linkhref{https://arxiv.org/abs/2508.01600}{arXiv}][\linkhref{https://arxiv.org/pdf/2508.01600}{PDF}]
\end{itemize}
{\footnotesize *Equal contribution among starred authors.}

\section{Software Projects}
\begin{itemize}[label={}, leftmargin=0pt]
    \item \textbf{openpi-eval} [\linkhref{https://github.com/branyang02/openpi-eval}{GitHub}, \linkhref{https://huggingface.co/datasets/brandonyang/metaworld_ml45}{Dataset}]: Built OpenPI evaluation infrastructure for a NeurIPS submission, supporting reproducible \texttt{pi05} rollouts across MetaWorld, LIBERO, LIBERO-Pro, RoboCasa, and RoboLab, plus \texttt{pi0\_fast} support where released and server-side inference batching.
    \item \textbf{openpi-cuda} [\linkhref{https://github.com/branyang02/openpi-cuda}{GitHub}]: Developed custom CUDA kernels with C++/Python bindings for $\pi_{0.5}$ VLA inference, reducing latency by 18.5ms versus the PyTorch baseline.
    \item \textbf{\href{https://notie-markdown.vercel.app/}{notie-markdown}} [\linkhref{https://notie-markdown.vercel.app/}{Website}]: Built a React/TypeScript markdown renderer with equation previewing, graphing, and code execution; shipped with a Python/Flask backend on Vercel and Heroku.
    \item \textbf{\href{https://github.com/branyang02/smart-oh}{SmartOH}} [\linkhref{https://github.com/branyang02/smart-oh}{GitHub}]: Built an office-hours queue management system with real-time queue updates, notifications, and analytics using Next.js, TypeScript, Python, and FastAPI; deployed with Vercel, AWS EC2, and CI/CD.
\end{itemize}

\section{Skills}
\begin{itemize}[label={}, leftmargin=0pt]
    \item \textbf{Programming}: Python, C++, CUDA C++, TypeScript/JavaScript, Java
    \item \textbf{ML \& Robotics}: PyTorch, JAX, Hugging Face, CUDA, Ray, Slurm, robot learning, VLA models
    \item \textbf{Web \& Infrastructure}: React, FastAPI, Flask, Docker, AWS EC2, Vercel, \verb|uv|, \verb|ruff|
\end{itemize}

\vfill
\noindent\textit{\small Last Updated: \today}
\end{document}
